|

### 2021-05-20 article/resubmission.Rmd
author affiliations

[^danilo]: Independent Researcher, <danilofreire@gmail.com>, <https://danilofreire.github.io>. Corresponding author.

@@

[^catarina]: PhD Student, University of California San Diego, <catarinamroman@gmail.com>, <http://catarinaroman.github.io>.

>>>>

[^danilo]: Senior Lecturer, School of Social and Political Sciences, University of Lincoln <danilofreire@gmail.com>, <https://danilofreire.github.io>. Corresponding author.

@@

[^catarina]: PhD Student, Department of Political Science, University of California San Diego, <catarinamroman@gmail.com>, <http://catarinaroman.github.io>.
